Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Experiment Setup

\section{Performance Evaluation}
In this section, we experimentally evaluate our FLPhish (noted as FLPhish(weight)) against untargeted attacks under different experiment settings. Furthermore, we compare FLPhish(weight)'s performance with FedAvg \cite{ref_01_GoogleFL}, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish(weight) outperforms these schemes in defending against Byzantine attacks. Furthermore, we compare our proposed aggregation rule, FLPhish(weight) with former aggregation rule used in our previous work \cite{li2021flphish}. Our previous work (noted as FLPhish($\tau$)) utilized a threshold to identify the Byzantine clients. Here we set the threshold to 0.1 (noted as FLPhish($\tau=0.1$)), 0.2 (noted as FLPhish($\tau=0.2$)) and 0.5 (noted as FLPhish($\tau=0.5$)).

@@

  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish(weight) under the circumstances of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
  \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} According to the previous research \cite{ref_06_model}, we distribute the data in a dataset among all the clients. Giving $M$ classes of data in a dataset, we split the clients into $M$ groups. A client $c$ in group $m$ is provided with data where data $m$ accounts for over $q$ percent. Within the same group, data are uniformly distributed among all the clients. The parameter $q$ controls the distribution inference of clients' local training data. If $q=\frac{1}{M}$, the clients' local training data are independent and identically distributed. We evaluate our FLPhish(weight) on three different $q$: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
  \subsubsection{{\textit{The number of clients}}} The number of clients is set to be 50 in our experiment.
  \subsubsection{{\textit{The local CNN model used by clients}}} ResNet is employed to perform deep learning tasks in our local client.
  \subsubsection{{\textit{The datasets {$d$}}}} We take three different datasets as our experiment datasets: \begin{itemize}
      \item MNIST: MNIST is a 10-class digit image classification dataset consisting of 60,000 training examples and 10,000 testing examples.
      \item Fashion-MNIST: Fashion-MNIST is a 10-class fashion image classification dataset. It has a predefined training set of 60,000 fashion images and a testing set of 10,000 fashion images.
      \item CIFAR-10: CIFAR-10 is a color image classification dataset. It has predefined 50,000 training examples and 10,000 testing examples. Each example belongs to one of the 10 classes.
  \end{itemize}

>>>>

\section{Performance Evaluation}
In this section, we experimentally evaluate our FLPhish (noted as FLPhish(weight) in the following parts) against untargeted attacks under different experiment settings. Furthermore, we compare FLPhish(weight)'s performance with FedAvg \cite{ref_01_GoogleFL}, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish(weight) outperforms these schemes in defending against Byzantine attacks. Furthermore, we compare our proposed aggregation rule, FLPhish(weight) with former aggregation rule used in our previous work \cite{li2021flphish}. Our previous work (noted as FLPhish($\tau$) in the following parts) utilized a threshold to identify the Byzantine clients. Here we set the threshold to 0.1 (noted as FLPhish($\tau=0.1$)), 0.2 (noted as FLPhish($\tau=0.2$)) and 0.5 (noted as FLPhish($\tau=0.5$)).

@@

  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish(weight) under the settings of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
  \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} We distribute the data in a dataset among all the clients, based on previous study \cite{ref_06_model}. If a dataset consists if $M$ classes of data, the FL clients will be divided into $M$ groups. Data is delivered to a client $c$ in group $m$, with data $m$ accounting for more than $q$ percent. Data is uniformly disseminated among all clients within the same group. The distribution inference of clients' local training data is controlled by the parameter $q$. If $q=\frac{1}{M}$, the clients' local training data are independent and identically distributed (IID). We evaluate our FLPhish(weight) on 6 different $q$ settings: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
  \subsubsection{{\textit{The number of clients}}} The number of clients is set to be 50 in our experiment.
  \subsubsection{{\textit{The local CNN model used by clients}}} ResNet is employed to perform deep learning tasks in our local client.
  \subsubsection{{\textit{The datasets {$d$}}}} We take three different datasets as our experiment datasets: \begin{itemize}
      \item MNIST: MNIST is a 10-class digit image classification dataset consisting of 60,000 training samples and 10,000 testing samples.
      \item Fashion-MNIST: Fashion-MNIST is a 10-class fashion image classification dataset. It has a predefined training set of 60,000 fashion images and a testing set of 10,000 fashion images.
      \item CIFAR-10: CIFAR-10 is a color image classification dataset. It has predefined 50,000 training examples and 10,000 testing examples. Each example belongs to one of the 10 classes.
  \end{itemize}
